\chapter{Project Description}

\section{Introduction}
\subsection{What is it?}

Our project is "Privacy-Preserving Cloud, Email and Password Systems", sponsored by OSU professor Attila Yavuz and his grad-student Thang Hoang.  As stated in the project posting, the motivation for this project is:

\begin{quote}
Storage service offered by cloud providers bring vast benefits to human society. However, this service also brings privacy concerns to the users. While the data privacy can be preserved by using standard encryption, it also prevents the user from querying the data on the cloud and thereby, invalidating the benefit of using cloud services. Thus, there is a need to develop a new cryptographic primitive that allows the user to query data outsourced to the cloud, while preserving its privacy.
\end{quote}

The goal of this project was to implement a DSSE scheme as a proof of concept to gather research information to better understand the strengths and limitation of these cryptographic primitives. Each member of our group was responsible for conceptually understanding the core of the DSSE scheme and were given individual areas to focus on during implementation: Andrew Ekstedt (Core implementation, Usability, and Troubleshoot), Scott Russell (Benchmarking, Communications), Scott Merrill (Optimizations, Codebreaker).
The role of our sponsor/client, Attila and Thang, was to oversee operations and provide advice and resources when needed. As a team we meet bi-weekly with out client to provide progress updates and to receive direction when possible issues arose.


% Definition and description of the problem you are trying to solve; be sure to
% write this problem definition for a general but educated audience
\section{Motivation}

    % Want to build tools that help protect privacy and fight mass surveillance

In today's technological world privacy is of key importance.
Faced with the growing public panic over mass surveillance,
companies have caught onto the significance of security and are creating products with strong encryption built in.
Web browser makers like Chrome and Mozilla are pushing for a secure-by-default world where every website has an SSL certificate, marking those without as untrusted.
Apple is positioning themselves as a privacy-conscious company by building strong encryption features into recent iPhone models.
Billions of users are flocking to secure chat apps like Signal and WhatsApp.

Despite these advances, there are many areas where security is lacking.
There is currently limited research into encrypted emails.
You can use GPG to encrypt messages, but then you lose the ability to quickly search your messages.
This problem can be addressed by giving your email provider a copy of your decryption keys, but now they have the ability to read all your email, defeating the purpose of encryption.
A similar problem exists for cloud storage systems: Google Drive will transparently encrypt your files for you, but Google necessarily hangs onto a copy of the encryption keys, which means that Google has the ability to decrypt your files any time they want.

    % No open-source implementation of searchable encryption

There has been some research into searchable encryption, but no open-source implementations of the algorithms that have been developed.
The need for a fast and efficient open-source implementation of dynamic searchable encryption is the basis for our research.

    % There's one that Cash did(?) but it's tied up in IP rights at IBM(?) and isn't available


\section{Goals}
% Proposed solution

% Primary goal is to demonstrate a practical implementation of searchable encryption

Our primary goal is to demonstrate a practical, open-source implementation of searchable encryption on a cloud provider.

    %Primary purpose is as a research project (proof of concept) rather than a polished product
    %Command-line interface is fine; we don't need a flashy ui, although that's a good stretch goal.
    %Also nice to have: mobile app

    %Attila and Thang have done published a research paper and done a preliminary implementation of a particular searchable encryption algorithm

    %Connect it to a cloud service like Amazon

%To convincingly demonstrate that searchable encryption is practical, it needs to work over a network.
Attila's research group has previously developed and implemented an algorithm for searchable encryption \cite{yavuz15},
however there is another scheme which was developed by David Cash which is asymptotically more efficient \cite{cash14}
in some areas; for example, the size of the encrypted index is smaller.
The source code for David Cash's implementation is not publicly available, so
our first project will be to build an open-source implementation of David Cash's scheme,
and to demonstrate that it works by building a client-server system that runs on Amazon EC2.

    %Need to figure out optimal data structure for actually using it? Says there are 10s of options publshed – need to get familiar with those
    %Will lean heavily on research by David Cash

%Part of the project will be to create a more efficient data structure, building on work by David Cash.
%One of the problems with the current solution is that the size of the index it stores is $\mathcal{O}(kf)$, where $k$ is the number of keywords, and $f$ is the number of documents.
%Which is huge.
%Since search indices are usually sparse, this wastes a ton of space.


    % Once that's working, want to hook it up to a database of emails

The second project is to apply our searchable encryption program to the problem of encrypted email.
This will probably involve writing a daemon which downloads messages from an email provider like gmail
and adds them to an encrypted database.
Presumably we would want to throw some email-specific UI and search functionality on top.
This part of the project is TBD and we expect to learn more about what is possible after we complete the first part of the project, and as we start working on this part.

    % Attila doesn't think this will be very difficult to set up once the first \^ project is done. I'm skeptical. Need to find out more details about what he has in mind.


% ORAM password manager
% (maybe)

A third project is to implement a password manager using ORAM (oblivious RAM),
which is a random-access data structure that hides memory access patterns from observers.
Current searchable encryption schemes leak some access patterns whenever you search,
so a password manager service implemented with such a scheme could learn for example that you always access a site at a certain time of day.
By obscuring the access patterns with ORAM, we can prevent the server from learning this information. This is a stretch goal
of the project and will be pursued if we have time after tackling the first two goals of this project. As it is not directly
related to David Cash's scheme.


\section{Metrics}
%Performance metrics: Tell how you will know when you have completed the project. Metrics help you and your client agree on what successful completion (e.g., faster, cheaper, easier to use, "a working prototype," a complete white paper with research results) of the project looks like.

There are two metrics, equally important: correctness and performance.

    % Correctness

The first metric is correctness.
The software should return the correct set of documents when searching for a keyword.
It should be able to dynamically add and delete files from the search index and return correct search results using the modified index.

    % Reasonable performance

The second metric is performance.
For the secure cloud, we want to aim for under a hundred milliseconds to search for a file. % more? less?
Attila has measured the previous implementation to be able to perform a search in around 10 milliseconds or less, even with an index containing millions of files, so this should be doable.
% other operations?
Performance for the email database is TBD.
% discussed with attila; he doesn't have specific requirements in mind,
% but expects to get a better idea after we've implemented some stuff
% and know what is possible
The password manager (if we get to it) will be less performant due to the overheads of ORAM, but we want to aim for 100 milliseconds.